\chapter{Recon Squad}

\emph{Recon Squad} is an unofficial variant of the~8th edition of
Games Workshop's \emph{Warhammer 40,000}, using the following rules to
play out small skirmishes with individual models.

\section{Army Selection}
\footname{Army Selection}

The following restrictions apply to the armies fielded by players in
Recon Squad games.

\begin{itemize}\shortlist
\item Army lists consist of a single Recon Squad Detachment of at
  most~200 points, selected according to Matched Play rules (e.g., all
  units must share a faction keyword).  Recon Squad detachments are
  comprised of~0--1 HQs,~0--2 Troops,~0--1 Elite,and~0--1 Fast Attack.
  As they are Battle-forged armies, Recon Squads receive the default~3
  Command Points (there is no detachment bonus).

\item You may include a single under-strength unit in the detachment,
  paying only the appropriate points to field one or more models and
  their wargear, rather than the standard minimum unit size.

\item Armies must include at least~4 models that are not Vehicles and
  may have at most~20 total models.

\item No models are permitted that have more than~6 wounds.

\item No models are permitted that have both a~2+ Armor save and~a 3+
  Invulnerable save.

\item No models or wargear are permitted that are restricted to a
  single instance (e.g., named characters).

%  \item Players with fully painted armies (3 color standard) gain a +1
%    in the roll-off for turn order.
  \end{itemize}
  
%\subsection{Traits}

%Some models are given special roles and abilities.

  \paragraph{Leader.} Each army's Leader is its non-Vehicle model with
  highest Leadership; designate one if several tie.

  \paragraph{Specialists.}  The Leader and~3 other non-Vehicle models
  are designated as Specialists.  Each is given a Specialist Trait
  from the following choices, with no repetitions, selected as part of
  the army list.

  \begin{itemize}\shortlist
  \item \emph{Brawler.} The model's Strength characteristic is
    improved by~2 and its Attacks characteristic by~1.

  \item \emph{Champion.} The model's Leadership characteristic is
    improved by~2.  It must take its Break Test first.  Any friendly
    model within 12'' may use its Leadership characteristic for their
    Break Tests.
    
  \item \emph{Duellist.} The model's~Weapon Skill characteristic is
    improved by~1, to a minimum of~2+.  For purposes of the Fight
    Phase this model is always considered to have charged this turn.

  \item \emph{Forward Observer.}  If this model does not advance,
    instead of shooting it may designate an enemy model within 12''
    and in its line of sight.  For the remainder of the phase, any hit
    rolls for shooting attacks made against the designated model may
    be re-rolled.

  \item \emph{Infiltrator.} The model may setup in deployment anywhere
    on the battlefield more than~9'' from the enemy deployment zone.
    Add an additional~1 to its saving throws whenever it gets a cover
    bonus.

%    Whenever this model gets a bonus to its saves
%    for being in cover, add~+2 instead of the usual~+1.
    
  \item \emph{Marksman.} The model's~BS characteristic is improved
    by~1, to a minimum of~2+, and AP for all its shooting attacks is
    improved by~1.
    
  \item \emph{Minelayer.}  If this model does not advance, instead of
    shooting it may place a mine marker within 3'' of itself on the
    battlefield.  Any enemy model that makes any move passing
    within~6'' of and visible to the mine marker immediately takes
    a~S5~AP--~D1 hit, rolled by the mine's player (and eligible
    for Command Re-Roll).  The mine is removed at the end of any phase in
    which it triggers at least once.

  \item \emph{Paramedic.} Roll a die whenever another friendly
    Infantry or Biker model within~3'' of this model loses its last
    wound.  On a~6+ the wound is ignored.
  \end{itemize}

\clearpage

\section{Gameplay Rules}

Recon Squad games follow Matched Play rules, with the following
changes and additions.

\subsection{Setup and General Play}

\paragraph{Skirmish.} Recon Squad skirmishes are played in~4'x4' or
3'x3' areas, as players or event organizers wish.

\paragraph{Army Of One.}  Before deployment, every model in the
player's army list is separated into its own unit.  These individual
model units are deployed and play as normal units for all game
purposes. Unless specifically noted otherwise in these rules the
original army list unit selections are not considered.

% \paragraph{No Holding Back.}  Models may not be set up off the
% battlefield unless specifically noted otherwise in the Recon Squad or
% mission rules.  All units that must be set up off the battlefield per
% their datasheet or codex rules but are not permitted to do so by these
% rules are deployed on the table the same as any other unit.

% \paragraph{First Turn.}
% Once deployment concludes, both players roll off, with the player that
% finished setting up their army first adding~+1 to their roll.  The
% winner may choose to play first or second.  If they take the first
% turn, their opponent may attempt to Seize the Initiative: On a D6 of 6
% they take first turn instead.

\paragraph{Help's Not Coming.}  No models beyond those in the army
lists may be added to the game in any way.

\paragraph{Side Effects.}  Rules conferred or applicable to the models
of an army list selection due to one model's special rule or wargear
are applicable to all the individual model units created from that
selection during deployment and when within~3'' of that model.

%\subsection{Stratagems}

%Recon Squads are Battle-forged and thus begin each game with the
%default~3 Command Points.  The following stratagems are additionally available:

%\begin{itemize}\shortlist
%\item \textit{Mushi.}
%\item \textit{Mushi.}
%\end{itemize}

\subsection{Movement Phase}

\paragraph{Everyone Falls The First Time.}
Models may jump freely across gaps in terrain narrower than their base
(or the model themselves if they have no base), simply expending the
movement distance to do so.

Models may attempt to jump across gaps in terrain of up to~6'' by
rolling a D6.  If the result is less than or equal to the breadth of
the gap in inches (rounding down), then the model falls.  Place it at
the bottom of the gap in contact with the near edge.  It immediately
suffers a Strength~X hit, where~X is the distance fallen in inches
(rounding up).  The vertical distance fallen does not count toward the
model's movement, and it may continue moving as usual if it survives.
If the roll is successful then the model may simply expend movement
distance to move across the gap as if it were a surface, but may not
end its move in the gap.

Any model may also jump down a vertical surface, applying the
preceding rules for a failed gap jump.

\subsection{Psychic Phase}

Remember that the Psychic Focus rule in Matched Play prohibits any
power other than Smite from being manifested more than once per turn,
regardless of the number of Psykers a player has.

\paragraph{Cast A Spell On You.}

Only a single model from each original army list unit selection with
the Psyker keyword may manifest a power per turn.  If their roll to do
so or the effects of that power are affected by the number of models
within their unit, then each model within 3'' from the original army
list unit selection counts.

For example, a unit of~6 Wyrdvane Psykers is selected as part of the
army and plays as~6 individual model units.  Each turn only one of
those models may manifest a power.  If all five other Wyrdvane Psykers
are within 3'' of that model then it receives a~+2 bonus to its roll
to manifest the chosen power.

\subsection{Shooting Phase}

\paragraph{No Heroes.} Characters may always be targeted for shooting
even if they are not the closest unit.  Hit rolls of~1 for any weapon
that could already do so, e.g., Sniper Rifles, may be re-rolled when
shooting Characters.

\paragraph{Unload.}  Attacks from ranged weapons may be divided and
allocated across multiple target units, provided each target is within
3'' of the first.  For example, a Heavy 3 weapon may be used to make
one attack each on three different targets, one attack on one target
and two on another within 3'', or three attacks on a single target.
All targets must be declared before any rolls to hit.

\paragraph{Frag Bag.} A model may only make a shooting attack with
grenades once per game per such wargear item.

\subsection{Endgame}

%\paragraph{Boots On The Ground.} Vehicles and buildings are
%not scoring units unless specifically noted so by mission rules.
%Embarked scoring units may score objective markers, measuring from the
%hull or main wall.

\paragraph{Breaking Point.}  From the start of a player's first turn
in which less than~50\% of their units remain, their army is
considered broken.  Before any other action, each of its units
starting with the Leader must take a Break Test.  Roll a D6 for each
unit and add the number of battle rounds in which their army has been
broken (starting at~1).  If the result exceeds their Leadership
characteristic the model is immediately removed from play.  Models
within~6'' of their Leader may use its Leadership; remember that the
Leader must test first.

% \paragraph{Sudden Death.}
% At the end of any turn after the first battle round, if one player has
% no models on the battlefield then the game ends immediately and their
% opponent automatically wins maximum victory points.

% and may choose to slaughter or save any remaining Civilians, for
% respectively~2 Infamy or~6 Fame each.

\paragraph{Variable Game Length.}
\underline{In an exception to Matched Play format, the Sudden Death
  rule does not apply.}  If a player is eliminated, their opponent
must continue to play and attempt to score mission objectives---you
can't win a maximal victory if you don't have enough units left to
hold the ground!  After battle round 5, the game continues on a D6
of~3+ by the first player.  Following battle round 6 the game
continues on a D6 of~4+ by the second player. No game continues past
battle round~7.



\section{Mission: Skirmish}

Vanguards patrolling the outskirts of their main forces have crashed
into each other!  Skirmish is the most basic, core Recon Squad
mission. Other scenarios are available at \url{rocketshipgames.com}.

\paragraph{The Battlefield.}  Deployment zones are diagonally opposite
corners of the battlefield, up to~12'' from the centerline between
them. Whichever player wins the roll-off to select deployment zones
may choose any of the four corners and their opponent takes the
opposite.  Place a total of three objective markers, one each at the
centers of the battlefield and the two battlefield quadrants outside
the deployment zones.

\paragraph{Primary Objectives.}
The outcome of this mission is determined by controlling objective
markers:

\begin{squishitemize}
\item \textbf{Major Victory:} Player controls at least two more
  objective markers than opponent.\hfill\emph{[10pts/0pts]}
\item \textbf{Minor Victory:} Player controls at least one more objective marker than opponent.\hfill \emph{[7pts/3pts]}
\item \textbf{Draw:} Players control equal objective markers.\hfill\emph{[5pts/5pts]}
\end{squishitemize}

\paragraph{Secondary Objectives.}
In addition, one bonus point is available for each of two secondary
objectives:

\begin{squishitemize}
\item Opponent's leader is a casualty.\hfill\emph{[+1pt]}
\item Player has models within~12'' of the two battlefield corners
  outside the deployment zones.\hfill\emph{[+1pt]}
\end{squishitemize}

\vfill
\hrule
\medskip
\noindent Recon Squad is completely unofficial, unauthorized, and
unaffiliated with Games Workshop.  Rules and text by Joe Kopena, cover
art by Luke Walker.  This is \emph{Recon Squad} 8th edition
release~\today.
